Grounding the Interaction: Anchoring Situated Discourse in Everyday Human-Robot Interaction

### 2011-10-19 paper_knowledge.tex
Fixed capitalization of titles to match stupid american rules

\title{Grounding the interaction: anchoring situated discourse in everyday human-robot interaction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Grounding human interaction into robot knowledge}

@@

\subsection{Related work}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{ORO, a knowledge management platform} \label{cognitivekernel}

\subsection{On knowledge representation} \label{knowledge_representation}

@@

\subsection{Reasoning and dynamic knowledge structuring}

@@

\subsection{ORO features}
\label{features}

@@

\subsubsection{Base functionalities}
\label{base}

@@

\subsubsection{Representation of alternative cognitive models}
\label{alterite}

@@

\subsubsection{Memory profiles}
\label{memory}

@@

\subsubsection{The events framework} 
\label{events}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Geometric reasoner for situation assessment}
\label{spark}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The natural language grounding process}
\label{dialog}

@@

\subsection{Informational content extraction}

@@

\subsection{Intentional content through verb resolution}
The sentence in the first example is built with the state verb \emph{be} at
indicative. Let us examine a different example with an action verb at
imperative mode (an order): ``Give me the banana". The process is
described in Figure~\ref{dialog|ex2}.

@@

\subsection{Informational content extraction requiring clarification}
\label{dialogs:disamb}
\begin{figure}
    \centering
	\begin{tabular}{p{7cm}}
	\emph{Initial knowledge model of} \texttt{human\_01}\\
	\hline
     	\hspace{0.3cm}\stmt{banana\_01 type Banana} \\
     	\hspace{0.3cm}\stmt{banana\_01 hasColor yellow} \\
     	\hspace{0.3cm}\stmt{banana\_02 type Banana} \\
     	\hspace{0.3cm}\stmt{banana\_02 hasColor green} \\
	\end{tabular} \\

@@

\subsection{\emph{Naming} experiment}
\label{naming}

@@

\subsection{\emph{Spy Game} experiment}
\label{spygame}

@@

\subsection{\emph{Moving to London} scenario}

@@

\subsubsection{Initial situation assessment}

@@

\subsubsection{Implicit disambiguation through visual perspective taking}
\label{exp:disambVPT}

@@

\subsubsection{Explicit disambiguation through verbal interaction and gestures}
\label{disamb-gestures}

@@

\subsection{Towards an event-driven, knowledge-oriented architecture for personal robotics}

@@

\subsubsection{Modeling the real world}

@@

\subsubsection{On thematic roles and action models}

@@

\subsubsection{Knowledge and embodiment}

>>>>

\title{Grounding the Interaction: Anchoring Situated Discourse in Everyday Human-Robot Interaction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Grounding Human Interaction Into Robot Knowledge}

@@

\subsection{Related Work}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{ORO, a Knowledge Management Platform} \label{cognitivekernel}

\subsection{On Knowledge Representation} \label{knowledge_representation}

@@

\subsection{Reasoning and Dynamic Knowledge Structuring}

@@

\subsection{ORO Features}
\label{features}

@@

\subsubsection{Base Functionalities}
\label{base}

@@

\subsubsection{Representation of Alternative Cognitive Models}
\label{alterite}

@@

\subsubsection{Memory Profiles}
\label{memory}

@@

\subsubsection{The Events Framework} 
\label{events}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Geometric Reasoner for Situation Assessment}
\label{spark}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Natural Language Grounding Process}
\label{dialog}

@@

\subsection{Informational Content Extraction}

@@

\subsection{Intentional Content Through Verb Resolution}
The sentence in the first example is built with the state verb \emph{be} at
indicative. Let us examine a different example with an action verb at
imperative mode (an order): ``Give me the banana". The process is
described in Figure~\ref{dialog|ex2}.

@@

\subsection{Informational Content Extraction Requiring Clarification}
\label{dialogs:disamb}
\begin{figure}
    \centering
	\begin{tabular}{p{7cm}}
	\emph{Initial knowledge model of} \texttt{human\_01}\\
	\hline
     	\hspace{0.3cm}\stmt{banana\_01 type Banana} \\
     	\hspace{0.3cm}\stmt{banana\_01 hasColor yellow} \\
     	\hspace{0.3cm}\stmt{banana\_02 type Banana} \\
     	\hspace{0.3cm}\stmt{banana\_02 hasColor green} \\
	\end{tabular} \\

@@

\subsection{\emph{Naming} Experiment}
\label{naming}

@@

\subsection{\emph{Spy Game} Experiment}
\label{spygame}

@@

\subsection{\emph{Moving to London} Scenario}

@@

\subsubsection{Initial Situation Assessment}

@@

\subsubsection{Implicit Disambiguation Through Visual Perspective Taking}
\label{exp:disambVPT}

@@

\subsubsection{Explicit Disambiguation Through Verbal Interaction and Gestures}
\label{disamb-gestures}

@@

\subsection{Towards an Event-Driven, Knowledge-Oriented Architecture for Personal Robotics}

@@

\subsubsection{Modeling the Real World}

@@

\subsubsection{On Thematic Roles and Action Models}

@@

\subsubsection{Knowledge and Embodiment}
